%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{resume} % Use the resume class

\usepackage[T1]{fontenc}
\usepackage{librefranklin}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif % Use the EB Garamond font

\usepackage[dvipsnames]{xcolor}

\usepackage{hyperref}

\hypersetup{
      colorlinks=true,% hyperlinks will be colored
      urlcolor=black,% hyperlink text will be black}
      urlbordercolor=black,% hyperlink borders will be black
}


%------------------------------------------------

\name{Sophia Campana} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{\underline{\smash{\href{https://sophmcamp.github.io/}{sophmcamp.github.io}}}~$\cdot$~\underline{\smash{\href{mailto:sophia_campana@aol.com}{sophia\_campana@aol.com}}}} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\large Education}
	
	\textbf{\underline{\smash{\href{https://www.vt.edu/}{Virginia Tech (Virginia Polytechnic Institute and State University)}}}} \hfill \normalfont{August 2023} \\ 
	\textit{BA in English – Professional and Technical Writing} \smallskip \\
\small	Honors Laureate, \textit{cum laude}, Overall GPA: 3.57
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\large Work Experience}

	\begin{rSubsection}{\underline{\smash{\href{https://www.digital-science.com/}{Digital Science}}}}{June 2025 - Present}{Product Specialist at Overleaf}{}\small
		\item Providing timely, professional, and empathetic email-based support to B2C and B2B users.
		\item Improving internal and user-facing documentation, educational resources, and training materials.
		\item Adhering to and refining established support processes to improve efficiency and effectiveness.
		\item Expanding expertise in technologies crucial to Overleaf users, such as \LaTeX, Dropbox, and R.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{\underline{\smash{\href{https://www.willowtreeapps.com/}{WillowTree, a TELUS Digital Company}}}}{October 2023 - March 2025}{Product Analyst}{}\small
		\item Contributed to the product development of a React Native redesign within the mobile app for one of Canada’s largest telecommunications companies and of a web-based application that integrates Virginia school readiness assessments.
		\item Wrote user stories, acceptance criteria, spikes, dependencies; hosted refinement meetings with frontend engineers, backend engineers, and testers; planned sprints with Delivery Lead and Engineering Lead.
		\item Created user workflow diagrams and wireframes and submitted test requests using REST APIs.
            \item Collaborated with designers on user needs, technical feasibility, copy, accessibility, and edge cases.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{\underline{\smash{\href{https://sciencelogic.com/}{ScienceLogic}}}}{June 2022 - August 2022 + June 2021 - August 2021}{Documentation Intern}{}\small
		\item Wrote, copyedited, and organized user manuals, release notes, and microcontent publicly available as webpages and PDFs for the company's AIOps monitoring systems through Git commits of XML files.
		\item Expanded upon listed duties by updating the documentation website’s CSS and JavaScript to improve user experience and to fix the functionality of navigating to older versions of the docs.
	\end{rSubsection}

%------------------------------------------------

    	\begin{rSubsection}{\underline{\smash{\href{https://orocktech.com/}{ORock Technologies}}}}{June 2020 - August 2020}{Technical Writer Intern}{}\small
		\item Assisted the federal sales team with white papers, discussion papers, and customer product data sheets.
		\item Copyedited and proofread proposals and slide decks in Microsoft PowerPoint, Publisher, and Word.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\large Volunteer Experience}

	\begin{rSubsection}{\underline{\smash{\href{https://c4osl.org/}{Center for Online Safety and Liberty}}}}{April 2025 - Present}{Webmaster}{}\small
		\item Updating WordPress core, themes, plugins with HTML and CSS; ensuring security and performance.
		\item Wrote a Python script using the Pandas and Stripe's API to migrate donors to a new e-commerce site.
	\end{rSubsection}
    
%------------------------------------------------

	\begin{rSubsection}{\underline{\smash{\href{https://c4kclubhouse.org/}{C4K (Computers4Kids)}}}}{September 2024 - Present}{1-to-1 Mentor}{}\small
		\item Helping mentees engage in hands-on activities and learn about coding, 3D modeling, and photography.
		\item Working together to produce and present a technology project; one of which was a virtual reality game.
	\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\large Technical Skills}
\small
	\begin{tabular}{@{}>{\bfseries} l @{\hspace{1ex}}l @{}}
		Languages: & Proficient in HTML, CSS, Markdown, \LaTeX, Java. Familiar with Python, R, JavaScript, React Native, Swift.\smallskip\\
		Tools: &  Overleaf, GitHub, AWS SageMaker Studio Lab, Jupyter, RStudio, Visual Studio Code, Eclipse, Figma,\\&Microsoft Office, Google Workspace, Lucidchart, Postman, WordPress, Miro, Logic Pro, iMovie, Max.\\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}